Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-09-21 AO_bondedSi.tex
Remove some paragraphs from Section 4, make some prose more concise.

\section{Laboratory demonstration: Embedding gaps of known sizes}

@@

We used the test pieces with known gaps to validate our measurement and analysis techniques.  We took transmission spectra of the bonded Si wafers and pucks, and the double side polished Si reference wafers using an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.  The measurement beam is about 1 mm $\times$ 10 mm The tool has a double monochromator, which reduces scattered light.

The Cary 5000 has four operation modes: single front, single back, double, and double reverse.  Double mode takes a reference spectrum simultaneously with the target spectrum.  We experimented with single front and double modes.  In principle double beam mode is 10 times more precise than single beam mode.  In practice, we found that double beam mode showed evidence for artifacts attributable to polarization differences between the two arms.  In this article, we therefore restrict the discussion to results obtained in single beam mode.  In both single and double mode, the spectrometer takes a baseline scan with no sample in the measurement holder.  We automatically divide sample spectra by this baseline spectrum.  In single beam mode, we must repeat the baseline measurements about every 10-30 minutes for post-process division.

We estimated the uncertainty and measurement repeatability experimentally.  We computed the RMS error and measurement repeatability in a single measurement by computing the standard deviation of a spectrum taken immediately after a baseline scan with no sample present.  We found that the mean value in single mode drifted by about 0.2\% over several measurements.  The standard deviation of the featureless spectrum was typically 0.02\% from point to point, with some portions of the spectrum demonstrating increased variance.  Table \ref{tabCary5000pars} summarizes the amplitudes of the drifts and individual measurement errors.  \emph{Correlated errors dominate the measurement uncertainty of our transmission spectra.}  The measurement uncertainty correlations are apparent in Figure \ref{figSiAbsorbfig}.  In some parts of the spectrum, the mean drift is about ten times larger than the local standard deviation of the spectrum.

The spectral sampling ranged from 2.0 to 10.0 nm.  We set the spectrometer slit width to produce a spectral resolution of 5.0 nm.  We expect smoothly varying spectral features for all conceivable interface gaps in Si bonded wafers.  Specifically, Fabry-P\'{e}rot fringes attributable to interfacial gaps in bonded Si will be well-sampled with 5 nm spectral resolution, so long as the interface gap is less than $\sim$100 $\mu$m.  This maximum gap limitation brings our technique to the point where it overlaps in capability with other techniques since the axial extents of such large gaps would be easily measurable by other means, like IR imaging and fringe-counting.

>>>>

\section{Embedding gaps of known axial and lateral extent}

@@

We used the test pieces with known gap sizes to validate our measurement and analysis techniques.  We took transmission spectra of the bonded Si wafers and pucks, and the double side polished Si reference wafers using an Agilent Cary 5000 UV-Vis-NIR spectrophotometer.  Table \ref{tabCary5000pars} lists the typical measurement settings and tool performance.

The measurement uncertainty in our experiments can be characterized by both its \emph{bias} and \emph{variance}.  The bias is equivalent to a mean-level drift, which may be attributable to monochromator lamp luminosity drift.  The variance is the random sample-to-sample measurement residual remaining once the bias term is removed.  In our experiments, the bias term has an amplitude of 0.2\%, whereas the variance has an amplitude of 0.02\%.  Our measurement uncertainty is dominated by bias, not variance.

%New prose here:
At this stage, \emph{any} regression technique can be employed to compare the model to data.  Least squares regression, and other popular methods can be applied, for example.  However, since least squares regression assumes zero bias term, we elected to apply a Gaussian process regression technique that can handle biased measurements.  Given the relatively small bias amplitude we measured, least squares regression and Gaussian process regression would likely yield similar solutions for the gap size, but least squares regression would drastically underestimate the uncertainty associated with the gap size\citep{DFMgp}.
